HGP analysis: fit model

### 2019-03-07 rick/1KGP.Rmd
update

```{r}
library(tidyverse)
library(lfa)
library(furrr)
library(broom)
library(tictoc)
options(future.globals.maxSize= 10000000000)
plan(multicore)
```

@@

@@

@@

```{r save_data}
saveRDS(data_list, "./data/preprocessed/data_fit.rds")
```

>>>>

```{r}
library(tidyverse)
library(lfa)
library(furrr)
library(broom)
library(tictoc)
options(future.globals.maxSize= 1000000000000)
plan(multicore)
```

@@

  saveRDS(data_iaf, "./data/preprocessed/iaf.rds")

@@

  saveRDS(data_list, "./data/preprocessed/data_list.rds")

@@

```{r save_data}
saveRDS(data_list, "./data/preprocessed/data_fits.rds")
```
